---
title: "Statistic Analysis of Race n Language Model"
date: "04/02/2022"
output:
  pdf_document: default
  word_document: default
  html_document: default
fontsize: 12pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(readxl)

library(tidyverse)
library(tidycensus)
library(dplyr)
library(ggplot2)
library(knitr)
library(qqplotr)

library(lattice)
library(survival)
library(Formula)
library(Hmisc)


library(Metrics)
library(lmtest)
library(fBasics)
library(segmented)

library(corrplot)
#library(raster)
#library(rgdal)
#library(classInt)
library(RColorBrewer)

library(oaxaca)
library(devtools)

library(viridis)#viridisLite provides the base functions for generating the color maps in base R 
library(GGally)
library(olsrr)
```


## 1. Description of Dataset

```{r}

Dataset_V4<- read_excel("Dataset_V4.xlsx", 
                         
    col_types = c("numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric","numeric",
        "numeric","numeric","numeric"))

Dataset_V4
#Rows: 210 Columns: 30
```
```{r}
glimpse(Dataset_V4)
#Rows: 210 Columns: 30
```

```{r}
df <- data.frame(Group=rep(c("Both Groups",  "Group 0","Group 1"), each=4),
                dose=rep(c("Uninsured Percentage by Tracts",  "Uninsured Percent of other race","Uninsured Percent of White alone","Percentage of Persons Who Speak English 'less than well'"),3),
                Uninsured_Percent=c(10.452,19.958,6.822,3.539,7.298,15.696,5.364,2.22,23.069,37.002,12.657,8.817))
head(df)
```
```{r}
png("barplot_Race.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
  
  df<-df %>%
  mutate(Category = fct_reorder(dose, Uninsured_Percent)) 
   
 ggplot2::ggplot(data=df, aes(x=Category, y=Uninsured_Percent, fill=Group)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Uninsured_Percent), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
    coord_flip() +
    ggtitle("The Means of Uninsured Percent in Minority Status") + 
  theme_minimal()


dev.off()
```

## 2. Correlation Analysis 


```{r}

cordata<-Dataset_V4%>%
  dplyr::select(c(Race_White_alone_Uninsured_Percent,Race_Hispanic_or_Latino_Uninsured_Percent,Persons_who_speak_English_less_than_well_Percent))
cordata

#210*3

```

```{r}
res <- rcorr(as.matrix(cordata))
view(res)
```

Extract the correlation coefficients
```{r}
Corr__Coefficients_Minority<- res$r
view(Corr__Coefficients_Minority)
write.csv(Corr__Coefficients_Minority, 'Corr_Coefficients_Minority.csv', row.names = FALSE)
```


```{r}
png("Corr_Coefficients_Minority.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
M <- cor(cordata)
corrplot(M, type = "upper", tl.pos = "td",
         method = "circle", tl.cex = 0.5, tl.col = 'black',
         order = "hclust", col=brewer.pal(n=8, name="RdYlBu"),diag = FALSE)
#ggsave("test.tiff", units="in", width=5, height=4, dpi=300, compression = 'lzw')
dev.off()

```


```{r}
ggpairs(cordata)
```

## 3. Regression Analysis

### 3.1 Minority Status Linear model using original dataset
a. Minority Status Linear model for both groups of rank80
```{r}
Minority__lmModel <- lm(Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=Dataset_V4)
summary(Minority__lmModel)
```
1. F-statistic: p-value: < 2.2e-16. The regression model fits the data better than the model with no independent variables.


2. Adjusted R-squared:  0.8856    Goodness-of-fit measure

3. Coefficients p-value. Coefficients are independent variables. The coefficients has effects on y.

Race_Hispanic_or_Latino_Uninsured_Percent          <2e-16 ***
Persons_who_speak_English_less_than_well_Percent   <2e-16 ***
Race_White_alone_Uninsured_Percent                 <2e-16 *** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1  





b. Minority Status Linear model for the rank80 0 group
```{r}
group0_data<-Dataset_V4%>%
  dplyr::filter(rank80 ==0) 
group0_data

```

```{r}
Minority0__lmModel <- lm(Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=group0_data)
summary(Minority0__lmModel)


```
1. F-statistic: p-value: < 2.2e-16. The regression model fits the data better than the model with no independent variables.


2. Adjusted R-squared:  0.8225  Goodness-of-fit measure

3. Coefficients p-value. Coefficients are independent variables. The coefficients has effects on y.


Race_Hispanic_or_Latino_Uninsured_Percent         < 2e-16 ***
Persons_who_speak_English_less_than_well_Percent 5.07e-13 ***
Race_White_alone_Uninsured_Percent                < 2e-16 ***



c. Minority Status Linear model for the rank80 1 group

```{r}

group1_data<-Dataset_V4%>%
  dplyr::filter(rank80 ==1) 
group1_data

```
```{r}

Minority1__lmModel <- lm(Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=group1_data)
summary(Minority1__lmModel)

```
1. F-statistic: p-value: < 4.483e-10. The regression model fits the data better than the model with no independent variables.


2. Adjusted R-squared:  0.6779   

3. Coefficients p-value. Coefficients are independent variables. The coefficients has effects on y.
Race_Hispanic_or_Latino_Uninsured_Percent        2.90e-05 ***
Persons_who_speak_English_less_than_well_Percent 5.00e-06 ***
Race_White_alone_Uninsured_Percent               2.37e-06 ***


### 3.2 Check if residuals are normally distributed and Box-Cox Transformation

Residuals are normally distributed.

Residuals are independent.

The mean of the residuals is zero and sum of the residuals is zero.

Residuals has constant variance.


a. Check Normality:The residuals of the model are normally distributed.

```{r}
jarqueberaTest(Minority__lmModel$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p <= 0.01  : very strong presumption against null hypothesis. It is not normally distributed

```{r}
jarqueberaTest(Minority0__lmModel$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p <= 0.01  : very strong presumption against null hypothesis. It is not normally distributed

```{r}
jarqueberaTest(Minority1__lmModel$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p > 0.01  : very strong presumption against null hypothesis. It is normally distributed

b.Box-Cox Transformation

```{r}
bc=boxcox(Minority__lmModel)
#extract best lambda
best.lam=bc$x[which(bc$y==max(bc$y))]
best.lam
```


Best lambda=0.5858586
We will transform Y with best lambda
"Linear Model With R" p134
```{r}
Dataset_V4<-Dataset_V4%>%
  dplyr::mutate(bestLambda_Total_Uninsured_Percent = (Total_Uninsured_Percent^0.5858586-1)/0.5858586)
Dataset_V4 <-Dataset_V4 %>% relocate(bestLambda_Total_Uninsured_Percent, .after = Total_Uninsured_Percent)
Dataset_V4
write.csv(Dataset_V4, 'Dataset_V4_BestLambda.csv', row.names = FALSE)

```

### 3.3 Minority Status Linear model using bestLambda_Total_Uninsured_Percent as y

a. Updated Minority Status Linear model for both groups of rank80
```{r}
Minority__lmModel_update <- lm(bestLambda_Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=Dataset_V4)
summary(Minority__lmModel_update)
```
```{r}
plot(Minority__lmModel_update)
```


```{r}
jarqueberaTest(Minority__lmModel_update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p <= 0.01  : very strong presumption against null hypothesis. It is not normally distributed



```{r}
ols_plot_resid_hist(Minority__lmModel_update)
```
Minority__lmModel_update uses a large sample (210 Ys which are bigger than 30), and the histogram of residuals is similar to normal distribution. According to Law of Large Numbers and Central Limit Theorem, we can accept the normality of residuals although the residuals are not normally distributed using Jarque - Bera Normalality Test.

b. Updated Minority Status Linear model for the rank80 0 group
```{r}
group0_data_update<-Dataset_V4%>%
  dplyr::filter(rank80 ==0) 
group0_data_update

```

```{r}
Minority0__lmModel__update <- lm(bestLambda_Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=group0_data_update)
summary(Minority0__lmModel__update)

```

```{r}
jarqueberaTest(Minority0__lmModel__update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p <= 0.01  : very strong presumption against null hypothesis. It is not normally distributed


```{r}
ols_plot_resid_hist(Minority0__lmModel__update)
```
Minority0__lmModel__update uses a large sample (168 Ys which are bigger than 30), and the histogram of residuals is similar to normal distribution. According to Law of Large Numbers and Central Limit Theorem, we can accept the normality of residuals although the residuals are not normally distributed using Jarque - Bera Normalality Test.


c. Updated Minority Status Linear model for the rank80 1 group
```{r}
group1_data_update<-Dataset_V4%>%
  dplyr::filter(rank80 ==1) 
group1_data_update

```

```{r}
Minority1__lmModel__update <- lm(bestLambda_Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent, data=group1_data_update)
summary(Minority1__lmModel__update)

```

```{r}
jarqueberaTest(Minority1__lmModel__update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p > 0.01  : very strong presumption against null hypothesis. It is normally distributed


Residual Normality Test

```{r}
ols_test_normality(Minority1__lmModel__update)
```
Kolmogorov-Smirnov p >0.05. Residuals of Minority1__lmModel__update are normally distributed.

Residual Diagnostics
https://cran.r-project.org/web/packages/olsrr/vignettes/residual_diagnostics.html



### 3.4 Other Residual Analysis of Updated Minority Status Linear Regression 


b. Check if residuals are independent.
```{r}
dwtest(Minority__lmModel_update)
```

The Durbin Watson statistic tests the hypothesis that there is no autocorrelation. If there is no autocorrelation (where subsequent observations are related), the Durbin-Watson statistic should be between 1.5 and 2.5 and the p-value will be above 0.05.
DW = 1.7277 (1.5<1.7277<2.5), p-value = 0.02086(0.02<0.05). 

```{r}
dwtest(Minority0__lmModel__update)
```
Residuals of Minority0__lmModel__update are independent.


```{r}
dwtest(Minority1__lmModel__update)
```
Residuals of Minority1__lmModel__update are independent.


c. The mean of the residuals is zero and sum of the residuals is zero.

```{r}
sum(Minority__lmModel_update$residuals)
```
```{r}
mean(Minority__lmModel_update$residuals)
```
The mean of the erros is zero and sum of the errors close to zero.

```{r}
sum(Minority0__lmModel__update$residuals)
```
```{r}
mean(Minority0__lmModel__update$residuals)
```
```{r}
sum(Minority1__lmModel__update$residuals)
```
```{r}
mean(Minority1__lmModel__update$residuals)
```


d.Check if residuals has constant variance.

A studentized residual is simply a residual divided by its estimated standard deviation.

A Breusch-Pagan Test is used to determine if heteroscedasticity is present in a regression analysis.

```{r}
bptest(Minority__lmModel_update)
```



```{r}
bptest(Minority0__lmModel__update)
```

```{r}
bptest(Minority1__lmModel__update)
```
The null hypothesis of the Breusch-Pagan test is homoscedasticity (= variance does not depend on auxiliary regressors). If the p-value becomes "small"(the p-value is less than 0.05), the null hypothesis is rejected. 


## 4. Oaxaca decomposition 
```{r}
oaxaca_Minority_results <- oaxaca(formula = bestLambda_Total_Uninsured_Percent ~  Persons_who_speak_English_less_than_well_Percent + Race_Hispanic_or_Latino_Uninsured_Percent+Race_White_alone_Uninsured_Percent|rank80, data = Dataset_V4)
names(summary(oaxaca_Minority_results))
summary(oaxaca_Minority_results)

```
```{r}
oaxaca_Minority_results$n
```
```{r}
oaxaca_Minority_results$y
```



### 4.1 Threefold decomposition
```{r}
oaxaca_Minority_results$threefold$overall
```
```{r}
plot(oaxaca_Minority_results, components = c("endowments","coefficients")) +
  labs(
    title = "Minority Status \nOaxaca Decomposition "
    )
```


```{r}
oaxaca_Minority_results$beta$beta.diff["Race_White_alone_Uninsured_Percent"]
```

### 4.2 Twofold decomposition
```{r}
oaxaca_Minority_results$twofold$overall
```

```{r}
plot(oaxaca_Minority_results, decomposition = "twofold", group.weight = -1)
```
```{r}
plot(oaxaca_Minority_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
"In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
variables = c("Race_Hispanic_or_Latino_Uninsured_Percent", "Persons_who_speak_English_less_than_well_Percent", "Race_White_alone_Uninsured_Percent"), variable.labels = c("Race_Hispanic_or_Latino_Uninsured_Percent"="Uninsured percent of race Hispanic or Latino","Persons_who_speak_English_less_than_well_Percent"= "Percent of persons who speak English less than well", "Race_White_alone_Uninsured_Percent" = "Uninsured percent of race white alone"))
```

```{r}
plot(oaxaca_Minority_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c("Race_Hispanic_or_Latino_Uninsured_Percent", "Persons_who_speak_English_less_than_well_Percent", "Race_White_alone_Uninsured_Percent"),
variable.labels = c("Race_Hispanic_or_Latino_Uninsured_Percent"="Uninsured percent of race Hispanic or Latino","Persons_who_speak_English_less_than_well_Percent"= "Percent of persons who speak English less than well", "Race_White_alone_Uninsured_Percent" = "Uninsured percent of race white alone"))
```

```{r}
variables <- c("Race_Hispanic_or_Latino_Uninsured_Percent", "Persons_who_speak_English_less_than_well_Percent", "Race_White_alone_Uninsured_Percent")
```

```{r}
columns <- c("group.weight", "coef(unexplained A)", "coef(unexplained B)")
```

```{r}
view(oaxaca_Minority_results$twofold$variables[[5]][variables, columns])
```









