---
title: "DataFrame V4.4 Statistic Analysis of Complete Model (ADI)"
date: "04/03/2022"
output:
  pdf_document: default
  word_document: default
  html_document: default
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(readxl)

library(tidyverse)
library(tidycensus)
library(dplyr)
library(ggplot2)
library(knitr)
library(qqplotr)

library(lattice)
library(survival)
library(Formula)
library(Hmisc)


library(Metrics)
library(lmtest)
library(fBasics)
library(segmented)

library(corrplot)
#library(raster)
#library(rgdal)
#library(classInt)
library(RColorBrewer)

library(oaxaca)
library(devtools)

library(viridis)#viridisLite provides the base functions for generating the color maps in base R 
library(GGally)

library(olsrr)

library(relaimpo)
```


## 1. Description of Dataset


```{r}

Dataset_V4<- read_excel("Dataset V4 Socioeconomic HouseCompo Multifactor2.xlsx", 
                         
    col_types = c("numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric","numeric",
        "numeric","numeric","numeric",
        "numeric","numeric","numeric"))

Dataset_V4
#Rows: 210 Columns: 33
```
```{r}
glimpse(Dataset_V4)
#Rows: 210 Columns: 33
```

Delete the rows from GEOID=="49035101400" because we miss the information in the ADI table.
```{r}
Dataset_V4.1<-Dataset_V4 %>% 
  dplyr::filter(GEOID!=49035101400)
write.csv(Dataset_V4.1, 'Dataset V4 Socioeconomic HouseCompo ADI.csv', row.names = FALSE)
Dataset_V4.1
#209 entries, 33 total columns
```


```{r}
df <- data.frame(Group=rep(c("Both Groups",  "Group 0","Group 1"), each=2),
                dose=rep(c("ADI(rank80)",  "ADI80"),3),
                State_Rank=c(4.679,4.679,3.904,3.84,7.76,8.337))
head(df)
```

```{r}
png("barplot_Mean_ADI.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
  
  df<-df %>%
  mutate(Category = fct_reorder(dose, State_Rank)) 
   
 ggplot2::ggplot(data=df, aes(x=Category, y=State_Rank, fill=Group)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=State_Rank), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
    coord_flip() +
    ggtitle("The Means of ADI State Rank in Groups") + 
  theme_minimal()


dev.off()
```

```{r}
df2 <- data.frame(Group=rep(c("Both Groups",  "Group 0","Group 1"), each=2),
                dose=rep(c("ADI(rank80)",  "ADI80"),3),
                Numbers_Group=c(209,209,167,170,42,39))
head(df2)
```

```{r}
png("barplot_Numbers_ADI.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
  
  df2<-df2 %>%
  mutate(Category = fct_reorder(dose, Numbers_Group)) 
   
 ggplot2::ggplot(data=df2, aes(x=Category, y=Numbers_Group, fill=Group)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Numbers_Group), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
    coord_flip() +
    ggtitle("The Numbers of Groups by ADI(rank80) and ADI80") + 
  theme_minimal()


dev.off()
```

## 2. Correlation Analysis 


Refer to: http://t  www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-using-r-software

```{r}

cordata<-Dataset_V4.1%>%
  dplyr::select(c(Race_White_alone_Uninsured_Percent,
                  Race_Hispanic_or_Latino_Uninsured_Percent,
                  Persons_who_speak_English_less_than_well_Percent,
                  
                  Native_Born_Uninsured_Percent,
                  Foreign_Born_Naturalized_Uninsured_Percent,
                  Foreign_Born_Not_citizen_Uninsured_Percent,
                  Less_than_high_school_graduate_Uninsured_Percent,
                  High_school_graduate_Uninsured_Percent,
                  Some_college_or_associate_degree_Uninsured_Percent,
                  Bachelor_or_higher_Uninsured_Percent,
                  Worked_Full_time_Uninsured_Percent,
                  Worked_less_FullTime_Uninsured_Percent,
                  Did_not_work_Uninsured_Percent,
                  Below_138_poverty_Uninsured_Percent, 
                  From_138_to_399_poverty_Uninsured_Percent,                             At_or_above_400_Poverty_Uninsured_Percent,
                  
                  Male_Uninsured_Percent,
                  Female_Uninsured_Percent,
                  AGE_Under_19_Uninsured_Percent,
                  AGE_19_to_64_Uninsured_Percent,                                        AGE_Above_65_Uninsured_Percent,
                  In_family_households_Uninsured_Percent,                               In_family_households_married_Uninsured_Percent,                         In_family_households_other_Uninsured_Percent,                           In_NonFamily_households_Uninsured_Percent,
                  
                  ADI80))
                                                       
cordata

#209*26

```

```{r}
res <- rcorr(as.matrix(cordata))
view(res)
```

Extract the correlation coefficients
```{r}
Corr__Coefficients_ADI<- res$r
view(Corr__Coefficients_ADI)
write.csv(Corr__Coefficients_ADI, 'Corr__Coefficients_ADI.csv', row.names = FALSE)
```


```{r}
png("Corr__Coefficients_ADI.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
M <- cor(cordata)
corrplot(M, type = "upper", tl.pos = "td",
         method = "circle", tl.cex = 0.5, tl.col = 'black',
         order = "hclust", col=brewer.pal(n=8, name="RdYlBu"),diag = FALSE)
#ggsave("test.tiff", units="in", width=5, height=4, dpi=300, compression = 'lzw')
dev.off()

```

```{r}
highcor_data<-Dataset_V4.1%>%
  dplyr::select(c(
                  Native_Born_Uninsured_Percent,
                  Worked_Full_time_Uninsured_Percent, 
                  Male_Uninsured_Percent,
                  AGE_19_to_64_Uninsured_Percent,
                  In_family_households_Uninsured_Percent,
                  In_family_households_married_Uninsured_Percent,
                  
                  
))
highcor_data
```
```{r}
highcor_res <- rcorr(as.matrix(highcor_data))
view(highcor_res)
```

```{r}
png("HighCorr_Coefficients_ADI.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
M <- cor(highcor_data)
corrplot(M, type = "upper", tl.pos = "td",
         method = "circle", tl.cex = 0.5, tl.col = 'black',
         order = "hclust", col=brewer.pal(n=8, name="RdYlBu"),diag = FALSE)
#ggsave("test.tiff", units="in", width=5, height=4, dpi=300, compression = 'lzw')
dev.off()

```

```{r}
ggpairs(highcor_data, title="High Correlation Coefficients in Complete Model
uninsured percent of native born
uninsured percent of worked full-time
uninsured percent of male
uninsured percent of age 19 to 64 years
uninsured percent of in family households
uninsured percent of in family households!!in married couple families") 
```

## 3. Regression Analysis

### 3.1 Complete Linear model using original dataset for both groups of rank80

```{r}
ADI__lmModel <- lm(Total_Uninsured_Percent~Race_Hispanic_or_Latino_Uninsured_Percent+Persons_who_speak_English_less_than_well_Percent+Race_White_alone_Uninsured_Percent+Native_Born_Uninsured_Percent+Foreign_Born_Naturalized_Uninsured_Percent+Foreign_Born_Not_citizen_Uninsured_Percent+Less_than_high_school_graduate_Uninsured_Percent+High_school_graduate_Uninsured_Percent+Some_college_or_associate_degree_Uninsured_Percent+Bachelor_or_higher_Uninsured_Percent+Worked_Full_time_Uninsured_Percent+Worked_less_FullTime_Uninsured_Percent+Did_not_work_Uninsured_Percent+Below_138_poverty_Uninsured_Percent+From_138_to_399_poverty_Uninsured_Percent+At_or_above_400_Poverty_Uninsured_Percent+Male_Uninsured_Percent+Female_Uninsured_Percent+AGE_Under_19_Uninsured_Percent+AGE_19_to_64_Uninsured_Percent+AGE_Above_65_Uninsured_Percent+In_family_households_Uninsured_Percent+In_family_households_married_Uninsured_Percent+In_family_households_other_Uninsured_Percent+In_NonFamily_households_Uninsured_Percent+ADI80,data=Dataset_V4.1)                                     
summary(ADI__lmModel)
```
```{r}
step(ADI__lmModel)
```

```{r}
highCorr__lmModel <- lm(Total_Uninsured_Percent~Native_Born_Uninsured_Percent+Worked_Full_time_Uninsured_Percent+Male_Uninsured_Percent+AGE_19_to_64_Uninsured_Percent+In_family_households_Uninsured_Percent+In_family_households_married_Uninsured_Percent,data=Dataset_V4.1)                                     
summary(highCorr__lmModel)


```

```{r}
metrics <- calc.relimp(highCorr__lmModel, type = c("lmg"), rela= TRUE)
metrics

#metrics <- calc.relimp(Socioeconomic__lmModel, type = c("lmg"), rela= TRUE)
#metrics
```



```{r}
Dataset_V4.1<-Dataset_V4.1%>%
  dplyr::mutate(NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor =  0.1651446*Native_Born_Uninsured_Percent+ 0.1477067*Worked_Full_time_Uninsured_Percent+ 0.1700372*Male_Uninsured_Percent+ 0.1798557*AGE_19_to_64_Uninsured_Percent+ 0.1833147*In_family_households_Uninsured_Percent+0.1539412*In_family_households_married_Uninsured_Percent)
Dataset_V4.1 <-Dataset_V4.1 %>% relocate(NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor, .after = AgeTo64_Sex_InFamilyHousehold_married_multifactor2)
write.csv(Dataset_V4.1, 'Dataset V4.1 Complete Analysis.csv', row.names = FALSE)
Dataset_V4.1
```


```{r}
cordata_multifactor<-Dataset_V4.1%>%
  dplyr::select(c(
                  NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor,
                  Race_White_alone_Uninsured_Percent,
                  Race_Hispanic_or_Latino_Uninsured_Percent,
                  Persons_who_speak_English_less_than_well_Percent,
                  Foreign_Born_Naturalized_Uninsured_Percent,
                  Foreign_Born_Not_citizen_Uninsured_Percent,
                  Less_than_high_school_graduate_Uninsured_Percent,
                  High_school_graduate_Uninsured_Percent,
                  Some_college_or_associate_degree_Uninsured_Percent,
                  Bachelor_or_higher_Uninsured_Percent,
                  Worked_less_FullTime_Uninsured_Percent,
                  Did_not_work_Uninsured_Percent,
                  Below_138_poverty_Uninsured_Percent, 
                  From_138_to_399_poverty_Uninsured_Percent,                          At_or_above_400_Poverty_Uninsured_Percent,
                  Female_Uninsured_Percent,
                  AGE_Under_19_Uninsured_Percent,                                     AGE_Above_65_Uninsured_Percent,                                                                  In_family_households_other_Uninsured_Percent,                           In_NonFamily_households_Uninsured_Percent,
                  ADI80))
                  
                  
cordata_multifactor
#209*21
```

```{r}
MultiFactor_res <- rcorr(as.matrix(cordata_multifactor))
view(MultiFactor_res)
```

Extract the correlation coefficients
```{r}
Corr__Coefficients_ADI_MultiFactor<- MultiFactor_res$r
view(Corr__Coefficients_ADI_MultiFactor)
write.csv(Corr__Coefficients_ADI_MultiFactor, 'Corr__Coefficients_ADI_MultiFactor.csv', row.names = FALSE)
```

```{r}
Hicordata_multifactor<-Dataset_V4.1%>%
  dplyr::select(c(
                  Worked_less_FullTime_Uninsured_Percent,
                  Female_Uninsured_Percent,
                  
                  NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor))                                      

Hicordata_multifactor
```


```{r}
ggpairs(Hicordata_multifactor, title="High Correlation Coefficients in Complete Model (2)
NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor
uninsured percent of worked less than full-time
uninsured percent of female ") 
```


```{r}
HighCorr__lmModel_multifactor2 <- lm(Total_Uninsured_Percent~Worked_less_FullTime_Uninsured_Percent+
                  Female_Uninsured_Percent+
                  NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor,data=Dataset_V4.1)
summary(HighCorr__lmModel_multifactor2)

```

```{r}
metrics <- calc.relimp(HighCorr__lmModel_multifactor2, type = c("lmg"), rela= TRUE)
metrics
```


```{r}
Dataset_V4.1<-Dataset_V4.1%>%
  dplyr::mutate(WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2 = 0.2524918* Worked_less_FullTime_Uninsured_Percent+ 0.3417357* Female_Uninsured_Percent+ 0.4057725* NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor)
Dataset_V4.1 <-Dataset_V4.1 %>% relocate(WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2, .after = AgeTo64_Sex_InFamilyHousehold_married_multifactor2)
write.csv(Dataset_V4.1, 'Dataset V4.1 Complete Analysis Multifactor2.csv', row.names = FALSE)
Dataset_V4.1
```

```{r}
cordata_multifactor2<-Dataset_V4.1%>%
  dplyr::select(c(WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2,
                  
                  Race_White_alone_Uninsured_Percent,
                  Race_Hispanic_or_Latino_Uninsured_Percent,
                  Persons_who_speak_English_less_than_well_Percent,
                  
                  
                  Foreign_Born_Naturalized_Uninsured_Percent,
                  Foreign_Born_Not_citizen_Uninsured_Percent,
                  Less_than_high_school_graduate_Uninsured_Percent,
                  High_school_graduate_Uninsured_Percent,
                  Some_college_or_associate_degree_Uninsured_Percent,
                  Bachelor_or_higher_Uninsured_Percent,
                  
                  
                  Did_not_work_Uninsured_Percent,
                  Below_138_poverty_Uninsured_Percent, 
                  From_138_to_399_poverty_Uninsured_Percent,                             At_or_above_400_Poverty_Uninsured_Percent,
                  
                  
                  
                  AGE_Under_19_Uninsured_Percent,
                                                        AGE_Above_65_Uninsured_Percent,
                                                                  In_family_households_other_Uninsured_Percent,                           In_NonFamily_households_Uninsured_Percent,
                  ADI80))
                  
cordata_multifactor2
#209*19
```
```{r}
MultiFactor_res2 <- rcorr(as.matrix(cordata_multifactor2))
view(MultiFactor_res2)
```

Extract the correlation coefficients
```{r}
Corr__Coefficients_ADI_MultiFactor2<- MultiFactor_res2$r
view(Corr__Coefficients_ADI_MultiFactor2)
write.csv(Corr__Coefficients_ADI_MultiFactor2, 'Corr__Coefficients_ADI_MultiFactor2.csv', row.names = FALSE)
```


```{r}
png("Corr__Coefficients_ADI_MultiFactor2.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
M <- cor(Corr__Coefficients_ADI_MultiFactor2)
corrplot(M, type = "upper", tl.pos = "td",
         method = "circle", tl.cex = 0.5, tl.col = 'black',
         order = "hclust", col=brewer.pal(n=8, name="RdYlBu"),diag = FALSE)
#ggsave("test.tiff", units="in", width=5, height=4, dpi=300, compression = 'lzw')
dev.off()

```



### 3.2 Box-Cox Transformation with multifactor 2 in both groups of rank80, group 0, and group 1

```{r}
ADI_Multifactor2__lmModel <- lm(Total_Uninsured_Percent~WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2+
                  Race_White_alone_Uninsured_Percent+
                  Race_Hispanic_or_Latino_Uninsured_Percent+
                  Persons_who_speak_English_less_than_well_Percent+
                  Foreign_Born_Naturalized_Uninsured_Percent+
                  Foreign_Born_Not_citizen_Uninsured_Percent+
                  Less_than_high_school_graduate_Uninsured_Percent+
                  High_school_graduate_Uninsured_Percent+
                  Some_college_or_associate_degree_Uninsured_Percent+
                  Bachelor_or_higher_Uninsured_Percent+
                  Did_not_work_Uninsured_Percent+
                  Below_138_poverty_Uninsured_Percent+
                  From_138_to_399_poverty_Uninsured_Percent+                           At_or_above_400_Poverty_Uninsured_Percent+
                  AGE_Under_19_Uninsured_Percent+
                  AGE_Above_65_Uninsured_Percent+
                  In_family_households_other_Uninsured_Percent+
                  In_NonFamily_households_Uninsured_Percent+
                  ADI80, data=Dataset_V4.1)
summary(ADI_Multifactor2__lmModel)
```
```{r}
bptest(ADI_Multifactor2__lmModel)
```


Box-Cox
```{r}
bc=boxcox(ADI_Multifactor2__lmModel)
#extract best lambda
best.lam=bc$x[which(bc$y==max(bc$y))]
best.lam
```
Best lambda=0.8282828
We will transform Y with best lambda
"Linear Model With R" p134
```{r}
Dataset_V4.1<-Dataset_V4.1%>%
  dplyr::mutate(bestLambda_ADI_Total_Uninsured_Percent = (Total_Uninsured_Percent^0.8282828-1)/0.8282828)
Dataset_V4.1 <-Dataset_V4.1 %>% relocate(bestLambda_ADI_Total_Uninsured_Percent, .after = Total_Uninsured_Percent)
Dataset_V4.1
write.csv(Dataset_V4.1, 'Dataset_V4_BestLambda_ADI.csv', row.names = FALSE)

```
```{r}
ADI_Multifactor2__lmModel_update <- lm(bestLambda_ADI_Total_Uninsured_Percent~WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2+
                  Race_White_alone_Uninsured_Percent+
                  Race_Hispanic_or_Latino_Uninsured_Percent+
                  Persons_who_speak_English_less_than_well_Percent+
                  Foreign_Born_Naturalized_Uninsured_Percent+
                  Foreign_Born_Not_citizen_Uninsured_Percent+
                  Less_than_high_school_graduate_Uninsured_Percent+
                  High_school_graduate_Uninsured_Percent+
                  Some_college_or_associate_degree_Uninsured_Percent+
                  Bachelor_or_higher_Uninsured_Percent+
                  Did_not_work_Uninsured_Percent+
                  Below_138_poverty_Uninsured_Percent+
                  From_138_to_399_poverty_Uninsured_Percent+                           At_or_above_400_Poverty_Uninsured_Percent+
                  AGE_Under_19_Uninsured_Percent+
                  AGE_Above_65_Uninsured_Percent+
                  In_family_households_other_Uninsured_Percent+
                  In_NonFamily_households_Uninsured_Percent+
                  ADI80, data=Dataset_V4.1)
summary(ADI_Multifactor2__lmModel_update)
```




```{r}
group0_data<-Dataset_V4.1%>%
  dplyr::filter(rank80 ==0) 
group0_data

```

```{r}
ADI0_Multifactor2__lmModel_update <- lm(bestLambda_ADI_Total_Uninsured_Percent~WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2+
                  Race_White_alone_Uninsured_Percent+
                  Race_Hispanic_or_Latino_Uninsured_Percent+
                  Persons_who_speak_English_less_than_well_Percent+
                  Foreign_Born_Naturalized_Uninsured_Percent+
                  Foreign_Born_Not_citizen_Uninsured_Percent+
                  Less_than_high_school_graduate_Uninsured_Percent+
                  High_school_graduate_Uninsured_Percent+
                  Some_college_or_associate_degree_Uninsured_Percent+
                  Bachelor_or_higher_Uninsured_Percent+
                  Did_not_work_Uninsured_Percent+
                  Below_138_poverty_Uninsured_Percent+
                  From_138_to_399_poverty_Uninsured_Percent+                           At_or_above_400_Poverty_Uninsured_Percent+
                  AGE_Under_19_Uninsured_Percent+
                  AGE_Above_65_Uninsured_Percent+
                  In_family_households_other_Uninsured_Percent+
                  In_NonFamily_households_Uninsured_Percent+
                  ADI80,data=group0_data)
summary(ADI0_Multifactor2__lmModel_update)


```



```{r}

group1_data<-Dataset_V4.1%>%
  dplyr::filter(rank80 ==1) 
group1_data

```


```{r}
ADI1_Multifactor2__lmModel_update <- lm(bestLambda_ADI_Total_Uninsured_Percent~WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2+
                  Race_White_alone_Uninsured_Percent+
                  Race_Hispanic_or_Latino_Uninsured_Percent+
                  Persons_who_speak_English_less_than_well_Percent+
                  Foreign_Born_Naturalized_Uninsured_Percent+
                  Foreign_Born_Not_citizen_Uninsured_Percent+
                  Less_than_high_school_graduate_Uninsured_Percent+
                  High_school_graduate_Uninsured_Percent+
                  Some_college_or_associate_degree_Uninsured_Percent+
                  Bachelor_or_higher_Uninsured_Percent+
                  Did_not_work_Uninsured_Percent+
                  Below_138_poverty_Uninsured_Percent+
                  From_138_to_399_poverty_Uninsured_Percent+                           At_or_above_400_Poverty_Uninsured_Percent+
                  AGE_Under_19_Uninsured_Percent+
                  AGE_Above_65_Uninsured_Percent+
                  In_family_households_other_Uninsured_Percent+
                  In_NonFamily_households_Uninsured_Percent+
                  ADI80,data=group1_data)
summary(ADI1_Multifactor2__lmModel_update)


```

### 3.3 Regression diagnosis

a. Residuals are normally distributed.

b. Residuals are independent.

c. The mean of the residuals is zero and sum of the residuals is zero.

d. Residuals has constant variance.


```{r}
jarqueberaTest(ADI_Multifactor2__lmModel_update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p > 0.01  : very strong presumption against null hypothesis. It is not normally distributed.

```{r}
plot(ADI_Multifactor2__lmModel_update)
```


```{r}
ols_plot_resid_hist(ADI_Multifactor2__lmModel_update)
```
```{r}
bptest(ADI_Multifactor2__lmModel_update)
```


```{r}
jarqueberaTest(ADI0_Multifactor2__lmModel_update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p > 0.01  : very strong presumption against null hypothesis. It is normally distributed


```{r}
ols_plot_resid_hist(ADI0_Multifactor2__lmModel_update)
```

```{r}
jarqueberaTest(ADI1_Multifactor2__lmModel_update$resid)
```
Null Hypothesis: Skewness and Kurtosis are equal to zero(normal distribution).  p > 0.01  : very strong presumption against null hypothesis. It is normally distributed



b. Check if residuals are independent.
```{r}
dwtest(ADI_Multifactor2__lmModel_update)
```

The Durbin Watson statistic tests the hypothesis that there is no autocorrelation. If there is no autocorrelation (where subsequent observations are related), the Durbin-Watson statistic should be between 1.5 and 2.5 and the p-value will be above 0.05.
DW = 1.9248 (1.5<1.9248<2.5), p-value =  0.2557(0.2557>0.05). 

```{r}
dwtest(ADI0_Multifactor2__lmModel_update)
```
Residuals of Socioeconomic0__lmModel__update are independent.
The Durbin Watson statistic tests the hypothesis that there is no autocorrelation. If there is no autocorrelation (where subsequent observations are related), the Durbin-Watson statistic should be between 1.5 and 2.5 and the p-value will be above 0.05.
DW = 1.8578 (1.5<1.8578<2.5), p-value =  0.1626(0.1626>0.05). 

```{r}
dwtest(ADI1_Multifactor2__lmModel_update)
```

The Durbin Watson statistic tests the hypothesis that there is no autocorrelation. If there is no autocorrelation (where subsequent observations are related), the Durbin-Watson statistic should be between 1.5 and 2.5 and the p-value will be above 0.05.
DW = 2.0394 (1.5<2.0394<2.5), p-value =  0.5024(0.5024>0.05). 

c. The mean of the residuals is zero and sum of the residuals is zero.

```{r}
sum(ADI_Multifactor2__lmModel_update$residuals)
```
```{r}
mean(ADI_Multifactor2__lmModel_update$residuals)
```
The mean of the erros is zero and sum of the errors close to zero.
```{r}
sum(ADI0_Multifactor2__lmModel_update$residuals)
```
```{r}
mean(ADI0_Multifactor2__lmModel_update$residuals)
```
```{r}
sum(ADI1_Multifactor2__lmModel_update$residuals)
```
```{r}
mean(ADI1_Multifactor2__lmModel_update$residuals)
```

d.Check if residuals has constant variance.


```{r}
bptest(ADI_Multifactor2__lmModel_update)
```


```{r}
bptest(ADI0_Multifactor2__lmModel_update)
```

```{r}
bptest(ADI1_Multifactor2__lmModel_update)
```



## 4. Oaxaca decomposition 
```{r}
oaxaca_ADI_results <- oaxaca(formula = bestLambda_ADI_Total_Uninsured_Percent~WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2+
                  Race_White_alone_Uninsured_Percent+
                  Race_Hispanic_or_Latino_Uninsured_Percent+
                  Persons_who_speak_English_less_than_well_Percent+
                  Foreign_Born_Naturalized_Uninsured_Percent+
                  Foreign_Born_Not_citizen_Uninsured_Percent+
                  Less_than_high_school_graduate_Uninsured_Percent+
                  High_school_graduate_Uninsured_Percent+
                  Some_college_or_associate_degree_Uninsured_Percent+
                  Bachelor_or_higher_Uninsured_Percent+
                  Did_not_work_Uninsured_Percent+
                  Below_138_poverty_Uninsured_Percent+
                  From_138_to_399_poverty_Uninsured_Percent+                           At_or_above_400_Poverty_Uninsured_Percent+
                  AGE_Under_19_Uninsured_Percent+
                  AGE_Above_65_Uninsured_Percent+
                  In_family_households_other_Uninsured_Percent+
                  In_NonFamily_households_Uninsured_Percent+
                  ADI80|rank80, data = Dataset_V4.1)
names(summary(oaxaca_ADI_results))
summary(oaxaca_ADI_results)

```
```{r}
oaxaca_ADI_results$n
```
```{r}
oaxaca_ADI_results$y
```



### 4.1 Threefold decomposition
```{r}
oaxaca_ADI_results$threefold$overall
```
```{r}
png("endowments_coefficients_complete.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, components = c("endowments","coefficients")) +
  labs(
    title = "Oaxaca Decomposition \n in Complete Model "
    )
dev.off()
```
```{r}
oaxaca_ADI_results$beta$beta.diff["WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2"]
```

```{r}
oaxaca_ADI_results$beta$beta.diff["Race_White_alone_Uninsured_Percent"]
```
```{r}
oaxaca_ADI_results$beta$beta.diff["Bachelor_or_higher_Uninsured_Percent"]
```


### 4.2 Twofold decomposition
```{r}
oaxaca_ADI_results$twofold$overall
```

```{r}
png("Twofold decomposition in Complete (ADI).png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1)
dev.off()
```
```{r}
png("Twofold decomposition2 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
"In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
variables = c(
 "WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2",
                  "Race_White_alone_Uninsured_Percent",
                  "Race_Hispanic_or_Latino_Uninsured_Percent",
                  "Persons_who_speak_English_less_than_well_Percent",
                  "Foreign_Born_Naturalized_Uninsured_Percent",
                  "Foreign_Born_Not_citizen_Uninsured_Percent",
                  "Less_than_high_school_graduate_Uninsured_Percent",
                  "High_school_graduate_Uninsured_Percent",
                  "Some_college_or_associate_degree_Uninsured_Percent",
                  "Bachelor_or_higher_Uninsured_Percent",
                  "Did_not_work_Uninsured_Percent",
                  "Below_138_poverty_Uninsured_Percent",
                  "From_138_to_399_poverty_Uninsured_Percent",                          "At_or_above_400_Poverty_Uninsured_Percent",
                  "AGE_Under_19_Uninsured_Percent",
                  "AGE_Above_65_Uninsured_Percent",
                  "In_family_households_other_Uninsured_Percent",
                  "In_NonFamily_households_Uninsured_Percent",
                  "ADI80"), variable.labels = c(
  "WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2"="Multifactor2 of Complete Model",
  "Race_White_alone_Uninsured_Percent"="Uninsured Percent of Race White alone",
  "Race_Hispanic_or_Latino_Uninsured_Percent"="Uninsured Percent of Race Hispanic or Latino",
  "Persons_who_speak_English_less_than_well_Percent"="Percent of Persons who speak English less than well",
  "Foreign_Born_Naturalized_Uninsured_Percent"="Uninsured Percent of Foreign-born Naturalized",
   "Foreign_Born_Not_citizen_Uninsured_Percent"="Uninsured Percent of Foreign-born Not citizen",
  "Less_than_high_school_graduate_Uninsured_Percent"="Uninsured Percent of Less than high school graduate",
  "High_school_graduate_Uninsured_Percent"="Uninsured Percent of High school graduate",
  "Some_college_or_associate_degree_Uninsured_Percent"="Uninsured Percent of Some college or associate degree",
  "Bachelor_or_higher_Uninsured_Percent"="Uninsured Percent of Bachelor or higher",
  "Did_not_work_Uninsured_Percent"="Uninsured Percent of Did not work",
  "Below_138_poverty_Uninsured_Percent"="Uninsured Percent of Below 138 poverty",
  "From_138_to_399_poverty_Uninsured_Percent"="Uninsured Percent of From 138 to 399 poverty",
  "At_or_above_400_Poverty_Uninsured_Percent"="Uninsured Percent of At or above 400 Poverty",
  "AGE_Under_19_Uninsured_Percent"="Uninsured Percent of AGE Under 19",
  "AGE_Above_65_Uninsured_Percent"="Uninsured Percent of AGE Above 65",
  "In_family_households_other_Uninsured_Percent"="Uninsured Percent of In family households other",
   "In_NonFamily_households_Uninsured_Percent"="Uninsured Percent of In Non-family households",
  "ADI80"="ADI80"))
dev.off()
```

```{r}
png("Twofold decomposition3 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  "WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2",
                  "Did_not_work_Uninsured_Percent",
                  "ADI80"),
variable.labels = c( "WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2"="Multifactor2 of Complete Model",
  "Did_not_work_Uninsured_Percent"="Uninsured Percent of Did not work",
  "ADI80"="ADI80"))
dev.off()
```

```{r}
png("Twofold decomposition4 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  
                  "Race_White_alone_Uninsured_Percent",
                  "Race_Hispanic_or_Latino_Uninsured_Percent",
                  "Persons_who_speak_English_less_than_well_Percent"
                  ),
variable.labels = c( 
  "Race_White_alone_Uninsured_Percent"="Uninsured Percent of Race White alone",
  "Race_Hispanic_or_Latino_Uninsured_Percent"="Uninsured Percent of Race Hispanic or Latino",
  "Persons_who_speak_English_less_than_well_Percent"="Percent of Persons who speak English less than well"
  ))
dev.off()
```

```{r}
png("Twofold decomposition5 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  
                  "Foreign_Born_Naturalized_Uninsured_Percent",
                  "Foreign_Born_Not_citizen_Uninsured_Percent"
                  ),
variable.labels = c( 
  "Foreign_Born_Naturalized_Uninsured_Percent"="Uninsured Percent of Foreign-born Naturalized",
   "Foreign_Born_Not_citizen_Uninsured_Percent"="Uninsured Percent of Foreign-born Not citizen"
  ))
dev.off()
```

```{r}
png("Twofold decomposition6 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  
                  "Less_than_high_school_graduate_Uninsured_Percent",
                  "High_school_graduate_Uninsured_Percent",
                  "Some_college_or_associate_degree_Uninsured_Percent",
                  "Bachelor_or_higher_Uninsured_Percent"),
variable.labels = c( 
  "Less_than_high_school_graduate_Uninsured_Percent"="Uninsured Percent of Less than high school graduate",
  "High_school_graduate_Uninsured_Percent"="Uninsured Percent of High school graduate",
  "Some_college_or_associate_degree_Uninsured_Percent"="Uninsured Percent of Some college or associate degree",
  "Bachelor_or_higher_Uninsured_Percent"="Uninsured Percent of Bachelor or higher"))
dev.off()
```

```{r}
png("Twofold decomposition7 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  
                  "Below_138_poverty_Uninsured_Percent",
                  "From_138_to_399_poverty_Uninsured_Percent",                          "At_or_above_400_Poverty_Uninsured_Percent"
                  ),
variable.labels = c( 
  "Below_138_poverty_Uninsured_Percent"="Uninsured Percent of Below 138 poverty",
  "From_138_to_399_poverty_Uninsured_Percent"="Uninsured Percent of From 138 to 399 poverty",
  "At_or_above_400_Poverty_Uninsured_Percent"="Uninsured Percent of At or above 400 Poverty"))
dev.off()
```

```{r}
png("Twofold decomposition8 in Complete (ADI) model.png", width = 220, height = 190, units='mm', res = 300)
  plot(1:10, 1:10, mar=c(3.5,0,3,0))
plot(oaxaca_ADI_results, decomposition = "twofold", group.weight = -1,
unexplained.split = TRUE, components = c("unexplained A",
"unexplained B"), component.labels = c("unexplained A" =
 "In Favor of Safe Group", "unexplained B" = "Against the Risk Group"),
component.left = TRUE, variables = c(  
                  "AGE_Under_19_Uninsured_Percent",
                  "AGE_Above_65_Uninsured_Percent",
                  "In_family_households_other_Uninsured_Percent",
                  "In_NonFamily_households_Uninsured_Percent"
                  ),
variable.labels = c( 
  "AGE_Under_19_Uninsured_Percent"="Uninsured Percent of AGE Under 19",
  "AGE_Above_65_Uninsured_Percent"="Uninsured Percent of AGE Above 65",
  "In_family_households_other_Uninsured_Percent"="Uninsured Percent of In family households other",
   "In_NonFamily_households_Uninsured_Percent"="Uninsured Percent of In Non-family households"
 ))
dev.off()
```


```{r}
variables <- c(
  "WorkLessFullTime_Female_NativeBorn_WorkFullTime_Male_Age19To64_InFamilyHouseholds_married_multifactor2",
                  "Race_White_alone_Uninsured_Percent",
                  "Race_Hispanic_or_Latino_Uninsured_Percent",
                  "Persons_who_speak_English_less_than_well_Percent",
                  "Foreign_Born_Naturalized_Uninsured_Percent",
                  "Foreign_Born_Not_citizen_Uninsured_Percent",
                  "Less_than_high_school_graduate_Uninsured_Percent",
                  "High_school_graduate_Uninsured_Percent",
                  "Some_college_or_associate_degree_Uninsured_Percent",
                  "Bachelor_or_higher_Uninsured_Percent",
                  "Did_not_work_Uninsured_Percent",
                  "Below_138_poverty_Uninsured_Percent",
                  "From_138_to_399_poverty_Uninsured_Percent",                          "At_or_above_400_Poverty_Uninsured_Percent",
                  "AGE_Under_19_Uninsured_Percent",
                  "AGE_Above_65_Uninsured_Percent",
                  "In_family_households_other_Uninsured_Percent",
                  "In_NonFamily_households_Uninsured_Percent",
                  "ADI80")
```

```{r}
columns <- c("group.weight", "coef(unexplained A)", "coef(unexplained B)")
```

```{r}
#write.csv(oaxaca_ADI_results$twofold$variables[[5]][variables, columns], 'Decomposition Complete Model.csv', row.names = FALSE)
view(oaxaca_ADI_results$twofold$variables[[5]][variables, columns])
```









